From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
add todo for number of properties

For the mapping between Freebase and Wikidata properties we have chosen to do it by hand
with the help of the Wikidata community.
With that, we have been able to quickly map around 360~properties
(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties).
For the mapping of properties where the domain are other topics or literals,
this mapping provides the Wikidata property to use.
We have also implemented a~special case for \texttt{/people/person/parents}
in order to be able to map them to Wikidata properties ``father'' and ``mother''
based on the person gender.
The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
because it is not possible to have a~\mbox{1-to-1} relationship
between Freebase and Wikidata properties: the CVT is linked to the subject topic by one property
and has properties pointing to its component values, whereas the Wikidata statement
has a~main property value group that is qualified by other such groups.
In order to map a~CVT to a~statement, we have to know which of the CVT's properties
should be used as the main value of the statement, with the others being mapped to qualifiers.
In order to keep a~simple mapping that associates one Wikidata property to one Freebase property,
we map both the property that links the topic to the CVT
and the main property of the CVT to the same Wikidata property, and, during the mapping process,
pick the latter as the main property of the CVT.
For example, if we map the CVT shown in \autoref{fig:cvt-obama},
we first use the Wikidata property \texttt{position held (P39)} to map
\texttt{/politician/government\_positions\_held} and
\texttt{/government\_position\_held/office\_position\_or\_title}.
Second, for the qualifiers, we use \texttt{start time (P580)}
for \texttt{/government\_position\_held/from} and \texttt{end time (P582)}
for\linebreak \texttt{/government\_position\_held/to}.
With the resulting property mapping, the created Wikidata statement
looks like the one presented in \autoref{fig:statement-obama}.

>>>>

For the mapping between Freebase and Wikidata properties we have chosen to do it by hand
with the help of the Wikidata community.
With that, we have been able to quickly map around 360~properties
(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties
\todo{This should probably have a date. As of today Wikidata has 1863 properties.}).
For the mapping of properties where the domain are other topics or literals,
this mapping provides the Wikidata property to use.
We have also implemented a~special case for \texttt{/people/person/parents}
in order to be able to map them to Wikidata properties ``father'' and ``mother''
based on the person gender.
The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
because it is not possible to have a~\mbox{1-to-1} relationship
between Freebase and Wikidata properties: the CVT is linked to the subject topic by one property
and has properties pointing to its component values, whereas the Wikidata statement
has a~main property value group that is qualified by other such groups.
In order to map a~CVT to a~statement, we have to know which of the CVT's properties
should be used as the main value of the statement, with the others being mapped to qualifiers.
In order to keep a~simple mapping that associates one Wikidata property to one Freebase property,
we map both the property that links the topic to the CVT
and the main property of the CVT to the same Wikidata property, and, during the mapping process,
pick the latter as the main property of the CVT.
For example, if we map the CVT shown in \autoref{fig:cvt-obama},
we first use the Wikidata property \texttt{position held (P39)} to map
\texttt{/politician/government\_positions\_held} and
\texttt{/government\_position\_held/office\_position\_or\_title}.
Second, for the qualifiers, we use \texttt{start time (P580)}
for \texttt{/government\_position\_held/from} and \texttt{end time (P582)}
for\linebreak \texttt{/government\_position\_held/to}.
With the resulting property mapping, the created Wikidata statement
looks like the one presented in \autoref{fig:statement-obama}.
